### 2014-03-07 src/methodology.Rnw
update

>>>>

\subsection{Operator Reduction}
% TODO expand as required

For operator reduction, we utilized the constrained mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
 and, Namin et al~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection.

\subsubsection{Constrained Mutation}
For this criteria, we used the two operators \textit{COND\_BOUNDARY, and NEGATE\_COND} which are similar to those given by Wong.
\subsubsection{Operator Selection}
We used the operators given by Offutt et al. \textit{INVERT\_NEGS, MATH, COND\_BOUNDARY,} \textit{NEGATE\_COND}, those given by Javalanche \textit{NEGATE\_COND, VOID\_METHOD\_CALLS, NON\_VOID\_METHOD\_CALLS, MATH, INLINE\_CONSTS, E\_MEMBER\_VARIABLE},  and by Namin et al.\textit{INVERT\_NEGS, MATH, INCREMENTS, NEGATE\_COND}. We also  compare N-Selective mutation as suggested by Offutt et al.

\subsection{Mutant Clustering}
For mutant clustering, we were unable to directly apply clustering based on distinct mutants as suggested by Hussain~\cite{hussain2008mutation}. However, we were able to apply clustering techniques on mutation operators, thus turning it to a set of selected operators.
